Collision rates of planetesimals near mean-motion resonances

### 2021-01-25 main.tex
Finish aaron's edits

\noindent \textbf{where  ($e_{1}$, $e_{2}$) and ($g_{1}$ , $g_{2}$) are the corresponding eigenvector components and eigenvalues of the matrix given by \citet{1999ssd..book.....M} (see ch 7, pg 276, equation 7.9 and 7.10, with $\alpha_{12} = \alpha$ and $\bar{\alpha_{12}} = 1$)}

% TODO: need to introduce matricies here, also mention that we are describing interaction between a planetesimal and jupiter here

\noindent \textbf{Here, $n$ is the mean motion of a body and $m$ is its mass. The frequency of the secular forcing is simply the difference of the two eigenvalue frequencies $g_{1} - g_{2}$. For the case of a Jupiter mass planet at 5.2 au perturbing a test particle at 3 au, the timescale for secular forcing is approximately 12,000 years.}

@@

\noindent where $\lambda = \varpi + M$ is the mean longitude of a
body, with $M$ being the mean anomaly. For bodies in resonance, the critical angle will librate around an 
equlibrium value, while this angle will circulate outside of resonance. For small eccentricities, this behavior is analogous to the motion of a 
pendulum. Furthermore, variations in the critical angle are coupled to changes in the mean motion and semimajor axis \citep{1999ssd..book.....M}. An important 
point to note, which we will revisit later, is that the variation frequency of this angle approaches zero near the edge of a resonance. The 
width of a resonance can be defined by determining the largest variation in semimajor axis that permits librational, rather than circulatory motion of $\phi$. For 
second order and higher MMRs, the maximum libration width is given by \citet{1999ssd..book.....M} \textbf{(ch. 8, pg 338, eq. 8.58} as

\noindent \textbf{For the most prominent interior mean-motion resonances, including the 2:1 and 3:1, the timescale associated with these oscillations driven by a Jupiter mass planet is  $\sim$ 1,000 - 2,000 years.}

@@

The sky model intensity (flux per pixel) is produced by interpolating the radial collision frequency onto a 2D Cartesian grid with cell widths of 
approximately 2 mas. In doing so, we choose to make the intensity proportional to the collision frequency (i.e., the dust) because it is the most 
straightforward case. Many different parameterizations are possible, depending on optical depth, grain size, disc temperature, etc., but we will avoid 
such complications here. We normalize the intensity by setting the total disc flux density to be 100 mJy at about 350 GHz.

@@

\textbf{We would again like to emphasize that the dust emission profiles in figure \ref{fig:alma_profiles} are constructed upon the assumption that the radial dust structure closely traces the collision profile of the planetesimals. This is only the case if the collisional cascade from which the dust grains form happens before radial drift has a chance to move debris away from the resonances. Although we showed with a back-of-the-envelope calculation (see section \ref{sec:dust}) that this is plausible for a typical protoplanetary disk with properties similar to the protosolar nebula, a more thorough treatment of collisional grinding is necessary to be able to interpret the dust emission profiles presented here as anything more than upper limits.}

@@

\appendix
\section{Nonaxisymmetric Structure in Boley 2017}\label{sec:boley_plot}

>>>>

\textbf{For the case of a Jupiter mass planet at 5.2 au perturbing a test particle at 3 au, the timescale for secular forcing is approximately 12,000 years. The details of this calculation
can be found in appendix \ref{sec:sec_forcing_timescale}.}

@@

\noindent where $\lambda = \varpi + M$ is the mean longitude of a
body, with $M$ being the mean anomaly. For bodies in resonance, the critical angle will librate around an 
equlibrium value, while this angle will circulate outside of resonance. For small eccentricities, this behavior is analogous to the motion of a 
pendulum. Furthermore, variations in the critical angle are coupled to changes in the mean motion and semimajor axis \citep{1999ssd..book.....M}. An important 
point to note, which we will revisit later, is that the variation frequency of this angle approaches zero near the edge of a resonance. The 
width of a resonance can be defined by determining the largest variation in semimajor axis that permits librational, rather than circulatory motion of $\phi$. 
\textbf{Calculations for the widths of first and second order interior MMRs are shown in appendix \ref{sec:libration}, along with a timescale for the libration. For the most prominent interior 
mean-motion resonances, including the 2:1 and 3:1, the timescale associated with these oscillations driven by a Jupiter mass planet is  $\sim$ 1,000 - 2,000 years.}

@@

The sky model intensity (flux per pixel) is produced by interpolating the radial collision frequency onto a 2D Cartesian grid with cell widths of 
approximately 2 mas. In doing so, we choose to make the intensity proportional to the collision frequency (i.e., the dust) because it is the most 
straightforward case. Many different parameterizations are possible, depending on optical depth, grain size, disc temperature, etc., but we will avoid 
such complications here\textbf{, as they would affect the overall brightness profile, but not the presence of any gaps or rings.} We normalize the intensity by
setting the total disc flux density to be 100 mJy at about 350 GHz.

@@

\textbf{We would again like to emphasize that the dust emission profiles in figure \ref{fig:alma_profiles} are constructed upon the assumption that the radial dust structure closely traces the collision profile of the planetesimals. For this assumption to be valid, the resulting dust must also remain locally confined, which is can be achieved achieved if the grains are reaccreted onto planetesimals \citep{2015SciA....1E0109J}. It is also necessary that the collisional cascade from which the dust grains form plays before radial drift has a chance to move debris away from the resonances. Although we showed with a back-of-the-envelope calculation (see section \ref{sec:dust}) that this is plausible for a typical protoplanetary disk with properties similar to the protosolar nebula, a more thorough treatment of collisional grinding and the subsequent evolution of the debris is necessary to be able to interpret the dust emission profiles presented here as anything more than upper limits.}

@@

\appendix
\section{Timescale for Secular Forcing}\label{sec:sec_forcing_timescale}

\noindent \textbf{where  ($e_{1}$, $e_{2}$) and ($g_{1}$ , $g_{2}$) are the corresponding eigenvector components and eigenvalues of a matrix, which describes the secular interaction between two bodies, given by \citet{1999ssd..book.....M} (see ch 7, pg 276, equation 7.9 and 7.10, with $\alpha_{12} = \alpha$ and $\bar{\alpha_{12}} = 1$)}

\noindent \textbf{Here, $n$ is the mean motion of a body and $m$ is its mass. In the case of a massless test particle being perturbed by a giant planet, $m_{0} = m_{g}$ and $m_{2} = 0$. The frequency of the secular forcing is simply the difference of the two eigenvalue frequencies $g_{1} - g_{2}$.}

\section{Libration in Mean Motion Resonance}\label{sec:libration}

For second order and higher MMRs, the maximum libration width is given by \citet{1999ssd..book.....M} \textbf{(ch. 8, pg 338, eq. 8.58} as

\section{Nonaxisymmetric Structure in Boley 2017}\label{sec:boley_plot}
